The development of anisotropy in an eroding porous medium

### 2018-06-07 docs/PhysicsPaper/StokesErosion.tex
Working on tex for PhysicsPaper
NM
Added fig2
Starting work on physics paper

\section{Introduction}
Stuff \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.5 \textwidth]{./Figs/shapes.pdf}
\caption{
Shapes.}
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

>>>>

\section{Introduction}

Effects of flow-induced erosion are visible across a range of scales in nature, from massive geological structures, to mesoscopic patterns, and finally down to the tiny granular constituents that comprise a porous medium. In the case of a porous medium specifically, it has been long recognized that bulk properties of mediums encountered in nature are typically anisotropic, so that the medium allows flow in a preferred direction more easily. This anisotropy is commonly attributed to how grains are deposited, with their longest dimension parallel to the settling bed, so that they allow flow preferentially in the horizontal direction. Controlled experiments, however, have not been performed to test this hypothesis. Here, we use highly-accurate numerical simulations to examine an alternative, and possibly complementary, mechanism: namely, that the flow-induced erosion of the medium's solid constituents contributes to its overall anisotropy.

Our method merges highly-efficient and highly-accurate boundary-integral methods with stable interface evolution methods to simulate the erosion of many solid-bodies in Stokes flow---the regime of groundwater flow. This method is documented, validated, benchmarked in \cite{quaife2018boundary}, and can practically simulate the erosion of order hundreds of solid bodies.

%Stuff to cite \cite{Ristroph2012, Moore2013, Huang2015, MooreCPAM2017} and other stuff \cite{Rycroft2016, Mitchell2016}.

\begin{comment}
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./Figs/fig1.pdf}
\caption{caption}
\label{fig1}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./Figs/fig2.pdf}
\caption{caption}
\label{fig2}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\end{comment}
